---
title: "TCRP Achilles Analysis"
author: "William Colgan"
date: "`r format(Sys.time(), '%d %B %Y')`"
output:
  github_document:
  html_notebook:
    theme: united
    toc: yes
    toc_float: yes
editor_options: 
  chunk_output_type: inline
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE, fig.width = 7, fig.height = 7, cache = T)

library(tidyverse)
library(viridis)
library(ggrepel)
```

```{r, include = F}
tcrp <- read_csv("./results/tcrp_achilles_results.csv")
tcrp_cor <- tcrp %>% group_by(gene,K) %>% summarise(test_cor_gene_mean = mean(test_cor_mean),test_cor_gene_sd = sd(test_cor_mean)) %>% 
  mutate(method = "TCRP")
rf <- read_csv("./results/k_shot_rf_achilles_results.csv")
rf_cor <- rf[grepl("mean correlation|Gene",names(rf))] %>% gather(key = "K",value = "test_cor_gene_mean",-Gene) %>% mutate(K = word(K))
rf_sd <- rf[grepl("stddev|Gene",names(rf))] %>% gather(key = "K",value = "test_cor_gene_sd",-Gene) %>% mutate(K = word(K))
rf_cor %<>% left_join(rf_sd,by = c("Gene","K")) %>% mutate(method = "Few_Shot_RF", gene = Gene, K = as.numeric(K)) %>%  select(-Gene)
rf_standard <- read_csv("./results/regular_rf_achilles_results.csv") %>% transmute(gene = Gene, test_cor_gene_mean = Correlation,method = "Standard_RF")
```

# Test correlation by K

Plots includes 464 genes with at least one 6 sigma outlier cell line. Points represent average across 5 trials for TCRP and 10 trials for few shot random forest for each gene and K value.

```{r fig.height= 5}
rbind(tcrp_cor,rf_cor) %>% ggplot(aes(x = as.factor(K),y = test_cor_gene_mean,fill = method)) + geom_boxplot() + xlab("K")
```

```{r}
tcrp_cor %>% left_join(rf_cor,by = c("gene","K"),suffix = c("_tcrp","_rf")) %>% 
  ggplot(aes(test_cor_gene_mean_tcrp,test_cor_gene_mean_rf,color = as.factor(K))) + 
  geom_point(size = .5) + geom_abline() + labs(color = "K") + lims(x = c(-.2,.6), y = c(-.2,.6))
```

# HNF1B

The paper reports HNF1B prediction performance of .6 for TCRP and .19 for random forest

```{r fig.height= 4}
rbind(tcrp_cor,rf_cor) %>% filter(gene == "HNF1B") %>% 
  ggplot(aes(x = as.factor(K),y = test_cor_gene_mean,color = method,group = method)) + geom_line() + geom_point(size = 4) + xlab("K") 
```

# Performance relative to standard random forest

Standard random forest uses the same features but uses standard five-fold cross validation. K value is fixed at 5 for both TCRP and few shot random forest.

## Few shot vs standard RF

```{r fig.height= 5}
bind_rows(rf_standard,rf_cor %>% filter(K == 5)) %>% ggplot(aes(method,test_cor_gene_mean,fill = method)) + geom_boxplot()
```

```{r}
df <- rf_standard %>% left_join(rf_cor %>% filter(K == 5),by = "gene",suffix = c("_rf_standard","_rf_5_shot"))
df %>% ggplot(aes(test_cor_gene_mean_rf_5_shot,test_cor_gene_mean_rf_standard)) + geom_point() + 
  geom_text_repel(data = df %>% filter(abs(test_cor_gene_mean_rf_5_shot - test_cor_gene_mean_rf_standard) > .3),aes(label = gene)) +
  geom_abline() + lims(x = c(-.3,.8), y = c(-.3,.8))
``` 

## TCRP vs standard RF

```{r fig.height= 5}
bind_rows(rf_standard,tcrp_cor %>% filter(K == 5)) %>% ggplot(aes(method,test_cor_gene_mean,fill = method)) + geom_boxplot()
```

```{r}
df <- rf_standard %>% left_join(tcrp_cor %>% filter(K == 5),by = "gene",suffix = c("_rf_standard","_tcrp_5_shot"))
df %>% ggplot(aes(test_cor_gene_mean_tcrp_5_shot,test_cor_gene_mean_rf_standard)) + geom_point() + 
  geom_text_repel(data = df %>% filter(abs(test_cor_gene_mean_tcrp_5_shot - test_cor_gene_mean_rf_standard) > .3),aes(label = gene)) +
  geom_abline() + lims(x = c(-.3,.8), y = c(-.3,.8))
``` 



